\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\usepackage{fancyhdr}
\setlength{\headheight}{14.5pt}
\addtolength{\topmargin}{-2.5pt}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhead[L]{GNOME Nepal - Social Media}
\fancyhead[R]{Meeting Minutes}
\fancyfoot[C]{\thepage}

\begin{document}

\begin{center}
    \textbf{\Large GNOME Nepal} \\[0.2cm]
    \textbf{Virtual Meeting Minutes} \\[0.2cm]
    Date: 6th November 2024 \\
    Time: 9:00 PM \\
\end{center}

\vspace{0.5cm}

\noindent\textbf{Agenda:}
\begin{enumerate}[label=\arabic*.]
    \item Formation and next steps for the social media and design team
    \item Types of content for social media posts
    \item Miscellaneous
\end{enumerate}

\vspace{0.5cm}

\noindent\textbf{Discussion Summary:}
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Formation and Next Steps for the Design Team}
    \begin{itemize}
        \item Two members, Roshan Pandey and Bikash Mishra, are interested in joining the social media and design team.
        \item Bikash Mishra will serve as the Social Media Manager, and Roshan including Bikash will take on the role of Designer.
        \item At least two additional designers are needed to complete the team.
        \item Discussions are ongoing with a designer who previously contributed to UbuCon India.
        \item The team will be responsible for creating and posting social media content.
        \item Post management will be organized in Notion.
        \item A new forum will be set up on Discord to gather post ideas from the community.
    \end{itemize}

    \item \textbf{Types of Content for Social Media Posts}
    \begin{itemize}
        \item Planned content includes:
        \begin{itemize}
            \item GNOME Nepal activities
            \item Upcoming meetings and sessions
            \item Updates on GNOME’s activities and customization options
            \item Information on Linux and other open-source technologies
            \item Tips and tricks for Linux and open-source usage
            \item Open-source news and events
            \item Quizzes and polls
        \end{itemize}
    \end{itemize}

    \item \textbf{Miscellaneous}
    \begin{itemize}
        \item A social media post template will be developed by next week.
        \item Posting strategy: daily posts in the evening for the first two months, followed by a shift to posting every other day.
    \end{itemize}
\end{enumerate}

\vspace{0.5cm}

\noindent\textbf{Conclusion:}
\begin{itemize}
    \item The social media and design team has been formed, with specific roles assigned.
    \item Planned content types and posting strategy have been outlined.
    \item A template for posts will be created to maintain a consistent brand image.
    \item Initial posting will be daily, transitioning to alternate days after two months.
\end{itemize}

\vspace{0.5cm}

\begin{center}
    \textbf{Keep Growing, Keep Learning, Keep Contributing}\\
    Minutes prepared by: \textbf{Roshan Pandey} \\
    \textbf{End of Minutes}
\end{center}

\end{document}
