\documentclass[a4paper,11pt]{article}
\usepackage{geometry}
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\usepackage{fancyhdr}
\setlength{\headheight}{14.5pt}
\addtolength{\topmargin}{-2.5pt}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhead[L]{GNOME Nepal Community Talk Event}
\fancyhead[R]{Meeting Minutes}
\fancyfoot[C]{\thepage}

\begin{document}

\begin{center}
    \textbf{\Large GNOME Nepal Community Talk Event} \\[0.2cm]
    \textbf{Virtual Meeting Minutes} \\[0.2cm]
    Date: November 1, 2024 \\
    Time: 9:00 PM \\
\end{center}

\vspace{0.5cm}

\noindent\textbf{Attendees:}
\begin{itemize}
    \item \textbf{Aaditya Singh} (President)
    \item \textbf{Sailesh Singh} (Member)
    \item \textbf{Nirjal Paudel} (Member)
    \item \textbf{Animesh Acharya} (Member)
    \item \textbf{Subash Ghimire} (Member)
    \item \textbf{Diwakar ...}(Member)
    \item \textbf{Utsav Bhattarai} (Member)
    \item \textbf{... Tamrakar} (Member)
    \item \textbf{Roshan Pandey} (Member)
    \item \textbf{Rupesh Nepal} (Member)
    \item \textbf{Manuj ...} (Member)
    \item \textbf {Prarambha Basyal} (Member)
    \item \textbf{Ritiks Thapa} (Member)
    \item \textbf{Aryan Chauhan} (Member)
    \item \textbf{Bikash Mishra} (Member)
    \item \textbf{Aaditya Thapa} (Member)
\end{itemize}

\vspace{0.5cm}

\noindent\textbf{Agendas:}
\begin{enumerate}[label=\arabic*.]
    \item Warm wishes for Tihar and Thanksgiving to the members.
    \item Updates on community repositories (if the update is to come from the maintainers).
    \item Updates on potential social team roles (Social Media Manager and Designer).
    \item Discussion on monthly virtual meetups and timing between physical meetups.
    \item Strategies for securing community sponsors.
    \item Planning sessions for after the festive season.
    \item Expanding sessions to reach students outside the valley.
    \item Updates on the UbuCon Asia 2025 bid.
\end{enumerate}

\vspace{0.5cm}

% new page
\newpage
\noindent\textbf{Discussion Summary:}
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Warm Wishes for Tihar and Thanksgiving:} \\
    \begin{itemize}
        \item Members exchanged warm wishes for Tihar and Thanksgiving.
        \item The community continues to grow strong and vibrant.
    \end{itemize}

    \item \textbf{Community Repositories Update:} \\
    \begin{itemize}
        \item The backend repository for the community website is ready and built on Django.
        \item Deployment is currently in progress on the infrastructure provided by GNOME.
        \item A potential session on React development was discussed.
        \item The backend infrastructure and event management process were demonstrated to the members.
        \item Swagger and Redoc were introduced to explain API documentation.
        \item No REST API was utilized in the current setup.
        \item The user panel interface was also shown to the members.
        \item Discussion on newsletter SMTP setup is forthcoming, with a dedicated meeting planned.
        \item Nirjal, Sailesh, and Rupesh are the designated maintainers of the repositories.
        \item The contributors repository was presented, and members were encouraged to contribute.
        \item A sponsor section has been added to the website.
        \item Documentation, including blogs and project sections, is currently being developed and will be updated soon.
        \item The contribution list is gradually increasing, and tracking contributions through GitHub issues is in place.
        \item Additional contributors are needed to support ongoing projects.
    \end{itemize}

    \item \textbf{Social Team Formation:} \\
    \begin{itemize}
        \item A social team will be formed to enhance community engagement.
        \item Roshan expressed interest in design and has ready assets.
        \item Bikash is interested in managing social media.
        \item A meeting will be scheduled to discuss the formation of this team.
        \item At least two members are needed for each team role.
        \item Responsibilities of the Social Media Manager include:
        \begin{itemize}
            \item Generating ideas for posts.
            \item Collaborating with others to create content.
            \item Focusing on GNOME and Linux-related posts to increase activity on social media.
        \end{itemize}
        \item Marketing efforts are also necessary to promote the community.
        \item Rupesh suggested that the Designer and Social Media Manager collaborate closely for effective content creation.
        \item The possibility of establishing a connection with RONB (Routine of Nepal Banda) will be discussed.
    \end{itemize}

    \item \textbf{Monthly and Physical Meetups:} \\
    \begin{itemize}
        \item Discussed holding both physical and virtual meetups to maintain consistent engagement.
        \item Plan to alternate between physical and virtual meetups with the gap of 2 weeks.
        \item Explored the possibility of holding physical meetups outside Kathmandu Valley, which would require sponsors in those areas.
        \item Proposed organizing physical meetups in major cities across each state to gradually expand the community’s reach.
        \item Emphasized the need to avoid making the community Kathmandu-centric by including members from various locations.
        \item Recognized that attendance at physical meetups may vary from virtual meetups.
        \item Acknowledged challenges in establishing strong leadership outside the valley and the importance of empowering members across Nepal to lead.
        \item Suggested holding a dedicated meeting focused on introducing and empowering new members in the GNOME Nepal Community.
        \item Proposed a plan to conduct sessions in different cities, potentially in partnership with local communities, with the aim of forming new community chapters if successful.
        \item Agreed on the need for a dedicated meeting to discuss community localization and expansion.
    \end{itemize}

    \item \textbf{Community Sponsors:} \\
    \begin{itemize}
        \item Discussed whether to seek sponsorship immediately or wait until UbuCon. Decided to wait.
        \item Suggested improving the sponsorship form and involving members in updating or refining it.
        \item Considered the role of the community as an intermediary in sponsorship efforts.
        \item Currently, the project is not ready to onboard contributors seeking sponsorship.
    \end{itemize}

    \item \textbf{Post-Festive Sessions:} \\
    \begin{itemize}
        \item Recognized the need to increase the number of instructors for upcoming sessions.
        \item A Git session was specifically requested by members.
        \item Formed a team with Bibek Dhakal, President of GDG Kathmandu, to support these sessions.
        \item A meeting will be held with instructors and potential supporters to ensure high-quality, valuable sessions.
        \item Sessions with softwarica, Kathmandu Engineering college (KEC), Kantipur Engineering college ( KEC ) and st. xaviers college (SXC) were discussed.
        \item A Git session at St. Xavier College was also proposed.
        \item A requirements document for session content and structure will be prepared.
        \item Pre-recorded training sessions for new instructors are planned to ensure consistency and quality.
        \item A dedicated instructor training session will be arranged, potentially at St. Xavier College.
        \item Session materials will be created and shared with community members.
        \item The community will send formal proposals to respective colleges and clubs for collaboration.
    \end{itemize}

    \item \textbf{Outreach Expansion:} \\
    \begin{itemize}
        \item Refer to the "Monthly and Physical Meetups" section for detailed outreach plans.
        \item Proposed creating Instagram Reels featuring new members outside the valley to increase community reach and engagement.
    \end{itemize}

    \item \textbf{UbuCon Asia 2025 Bid:} \\
    \begin{itemize}
        \item The UbuCon Asia 2025 bid has been submitted.
        \item Changes requested by the international community were made and resubmitted.
        \item The final decision on the bid will be made next week, as the main review team is currently occupied in Netherlands.
        \item Ubuntu India has expressed interest in supporting the community.
        \item A potential for self-sponsored speakers was mentioned by a contact in the USA.
        \item Ubuntu Korea has also shown interest in supporting the event.
    \end{itemize}

    
    \item \textbf{Miscellaneous:} \\
    \begin{itemize}
        \item Discussed establishing connections with major media outlets to highlight international ties with Nepal.
        \item Emphasized that the main focus of the community is on encouraging contributions.
        \item Mentioned Google Summer of Code (GSoC) and its benefits for members.
    \end{itemize}

\end{enumerate}

\vspace{0.5cm}
\newpage
\noindent\textbf{Next Meetings:} 
\begin{itemize}
    \item Dedicated meeting planned for discussing newsletter SMTP setup and Kubernetes integration.
    \item Upcoming meeting to finalize the formation of the social media and design teams.
    \item Agreed on scheduling a meeting focused on community localization and expansion strategies.
    \item Meeting with instructors and potential supporters to ensure session quality and value.
    \item Pre-recorded training sessions for new instructors are planned to maintain session consistency.
    \item Potential instructor training session at St. Xavier College.
\end{itemize}


\noindent\textbf{Conclusion:} \\
\begin{itemize}
    \item The meeting covered important updates and plans, focusing on community growth, event preparation, and increased engagement.
    \item Agreed to continue efforts toward enhancing member participation, outreach, and partnerships.
    \item Members are encouraged to keep contributing actively and to prepare for the upcoming initiatives.
\end{itemize}
\hfill\\
\hfill \\
\begin{center}
    \textbf{Keep Growing, Keep Learning, Keep Contributing}\\
    Minutes Prepared by: \textbf{Roshan Pandey} \\
    \textbf{End of Minutes}
\end{center}

\end{document}